SPARQL on the Open, Decentralised Web

### 2016-11-16 dissertation/conclusions.tex
add jurgen-paper on data summary
Expand on the conclusions, fixes #24

Problems~\ref{prob:unknowndist},~\ref{prob:unknownconddist}~and~\ref{prob:largestats}
has a promising approach in \cite{5767868}, but a way to expose this
information to a client or a proxy is lacking. We saw in
\cite{splendid} that a VoID description can be used with some success,
but this needs further elaboration.

@@

\begin{itemize}
\item Hypermedia is one key to developing applications on the Semantic
  Web.
\item Traits ease the task of developing experimental systems and
  usage of optimisations in underlying systems.
\item While the adoption of caching and conditional requests as defined
  in HTTP is not widespread, the adoption is sufficient to start using
  them in practical systems.
\item Evaluation methodologies suffer from a poor foundation in
  philosophy of science, and research into the epistemology of the
  field is important.
\item The author admits that the study is lacking in terms of
  objectivity, but notes that the problems are of a general nature.
\item Statistical Design of Experiments provides a path to a critical
  practice of evaluations, needed to improve the foundations of the
  field.
\end{itemize}

>>>>

Problems~\ref{prob:unknowndist},~\ref{prob:unknownconddist}~and~\ref{prob:largestats}
has a promising approach in \cite{5767868}, but a way to expose this
information to a client or a proxy is lacking. We saw in
\cite{splendid} that a VoID description can be used with some success,
but this needs further elaboration. Histograms have also been proposed
for this purpose in \cite{Umbrich2011}.

@@

The conclusions of the papers can be summarised as follows:

Hypermedia can contribute a ``View Source'' capability to application
development and data exploration, and thinking about an RDF statement
with control information as a natural language sentence can make RDF
understandable to many developers. Therefore, it is one key to
developing applications on the Semantic Web.

When engineering systems to encourage contributions from many
different parties, it is important to carefully consider how such
systems can be extended and adapted, and how contributions can be made
a part of the systems and so enhance the base that researchers and
other users can benefit from. Traits ease the task of extending
database systems with experimental features and eases the usage of
optimisations in underlying systems.

Caching in the Web is a prominent topic, but we found that while the
adoption of caching and conditional requests as defined in HTTP is not
widespread, the adoption is sufficient to start using them in
practical systems. We also found that many resources change at a very
slow pace, but that it is not reflected in the freshness lifetime set
by the server, but may more commonly be computed by common heuristics.

Evaluation methodologies suffer from a poor foundation in philosophy
of science, and research into the epistemology of the field is
important. This is due to several interrelated factors: The field of
research differs from natural science in that it studies a human
artefact that does not yet exist. An example of this problem is that
there is no formulated coherent theory of the Semantic Web, so the
external validity of any hypothesis relative to such a theory can
always be contested. If one would wish to follow the criterion that
science is distinguished by falsifiability, it is currently difficult
to tell if the evaluation or the hypothesis is to be rejected.

Moreover, along the above directions, and based on the fact that the
author has a large intellectual investment in the success of the
Semantic Web, the author admits that the study is lacking in terms of
objectivity, but notes that the problems are of a general nature.

Empirical evaluations should be developed from the principles of
philosophy of science and statistics, and the practice of benchmarking
does not adequately follow these principles. Statistical Design of
Experiments provides a path to a critical practice of evaluations,
needed to improve the foundations of the field. The experiment we
designed provided for both an instructive example of a new methodology
and how to use the methodology to evaluate the experiment itself.
